---
title: "group project final"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
require(plyr)
require(dplyr)
require(tidyverse)
require(ggplot2)
require(stargazer)
require(rpart)
require(rpart.plot)
require(class)
require(caret)
library(lme4)
library(haven)
require(haven)
require(lme4)
```

# GROUP PROJECT FINAL : Rosairi Estevez and Chris Lacroix

## PSY V0500; Kevin Foster



### `SIMPLE STATS MH NEED and GET`

```{r}
NN <- length(Household_Pulse_data$SEXUAL_ORIENTATION)
set.seed(12345)
restrict_1 <- (runif(NN) < 0.3) #just use 30%
summary(restrict_1)
```


```{r}
Householdsmall <- subset(Household_Pulse_data, restrict_1)
```

```{r}
Householdsmall$MHLTH_NEED <- recode(Householdsmall$MHLTH_NEED, "NA" = NULL, "all children need mental health treatment" = 1, "some but not all children" = 1, "no, none of the children" = 2)
```



```{r}
Householdsmall$MHLTH_GET <- recode(Householdsmall$MHLTH_GET, "NA" = NULL, "all children get the mental health treatment they need" = 1, "some but not all children" = 1, "no, none of the children" = 2)
```



```{r}
summary1 <- ddply(Householdsmall,.(SEXUAL_ORIENTATION), summarize, mean_mentalhealth = mean(MHLTH_NEED, na.rm = TRUE), sd_mentalhealth = sd(MHLTH_NEED, na.rm = TRUE), n_obs = sum(!is.na(MHLTH_NEED)) )

summary1
```


```{r}
summary2 <- ddply(Householdsmall,.(SEXUAL_ORIENTATION), summarize, mean_mentalhealth = mean(MHLTH_GET, na.rm = TRUE), sd_mentalhealth = sd(MHLTH_GET, na.rm = TRUE), n_obs = sum(!is.na(MHLTH_GET)) )

summary2
```
```{r}
summary(Householdsmall$MHLTH_NEED[Householdsmall$SEXUAL_ORIENTATION == "gay or lesbian"])
```

```{r}
summary(Householdsmall$MHLTH_NEED[Householdsmall$SEXUAL_ORIENTATION == "bisexual"])
```

```{r}
summary(Householdsmall$MHLTH_NEED[Householdsmall$SEXUAL_ORIENTATION == "something else"])
```

```{r}
summary(Householdsmall$MHLTH_NEED[Householdsmall$SEXUAL_ORIENTATION == "dont know"])
```

```{r}
summary(Householdsmall$MHLTH_NEED[Householdsmall$SEXUAL_ORIENTATION == "straight"])
```


```{r}
summary(Householdsmall$MHLTH_GET[Householdsmall$SEXUAL_ORIENTATION == "gay or lesbian"])
```

```{r}
summary(Householdsmall$MHLTH_GET[Householdsmall$SEXUAL_ORIENTATION == "straight"])
```

```{r}
summary(Householdsmall$MHLTH_GET[Householdsmall$SEXUAL_ORIENTATION == "bisexual"])
```

```{r}
summary(Householdsmall$MHLTH_GET[Householdsmall$SEXUAL_ORIENTATION == "something else"])
```

```{r}
summary(Householdsmall$MHLTH_GET[Householdsmall$SEXUAL_ORIENTATION == "dont know"])
```




### `SIMPLE STATS ANXIOUS and DOWN`

```{r}
Householdsmall$ANXIOUS <- recode(Householdsmall$ANXIOUS, "NA" = NULL, "no anxiety over past 2 wks" = 0, "several days anxiety over past 2 wks" = 1, "more than half the days anxiety over past 2 wks" = 2, "nearly every day anxiety" = 3)
```

```{r}
Householdsmall$DOWN <- recode(Householdsmall$DOWN, "NA" = NULL, "no days in past 2 wks feeling depressed" = 0, "several days over past 2 wks" = 1, "more than half the days over past 2 wks" = 2, "nearly every day" = 3)
```


```{r}
summary3 <- ddply(Householdsmall,.(SEXUAL_ORIENTATION), summarize, mean_depression = mean(DOWN, na.rm = TRUE), sd_depression = sd(DOWN, na.rm = TRUE), n_obs = sum(!is.na(DOWN)) )

summary3
```

```{r}
summary(Householdsmall$DOWN[Householdsmall$SEXUAL_ORIENTATION == "gay or lesbian"])
```

```{r}
summary(Householdsmall$DOWN[Householdsmall$SEXUAL_ORIENTATION == "bisexual"])
```

```{r}
summary(Householdsmall$DOWN[Householdsmall$SEXUAL_ORIENTATION == "something else"])
```

```{r}
summary(Householdsmall$DOWN[Householdsmall$SEXUAL_ORIENTATION == "dont know"])
```

```{r}
summary(Householdsmall$DOWN[Householdsmall$SEXUAL_ORIENTATION == "straight"])
```

```{r}
summary4 <- ddply(Householdsmall,.(SEXUAL_ORIENTATION), summarize, mean_anxiety = mean(ANXIOUS, na.rm = TRUE), sd_anxiety = sd(ANXIOUS, na.rm = TRUE), n_obs = sum(!is.na(ANXIOUS)) )

summary4
```

```{r}
summary(Householdsmall$ANXIOUS[Householdsmall$SEXUAL_ORIENTATION == "bisexual"])
```

```{r}
summary(Householdsmall$ANXIOUS[Householdsmall$SEXUAL_ORIENTATION == "gay or lesbian"])
```

```{r}
summary(Householdsmall$ANXIOUS[Householdsmall$SEXUAL_ORIENTATION == "something else"])
```

```{r}
summary(Householdsmall$ANXIOUS[Householdsmall$SEXUAL_ORIENTATION == "dont know"])

```

```{r}
summary(Householdsmall$ANXIOUS[Householdsmall$SEXUAL_ORIENTATION == "straight"])
```


### `GRAPHS`

```{r}
select1 <- (Household_Pulse_data$MHLTH_NEED != "NA")
Household_kids <- subset(Household_Pulse_data,select1)
```

```{r}
levels(Household_Pulse_data$MHLTH_NEED)
```


```{r}
Household_kids$MHLTH_NEED <- fct_recode(Household_kids$MHLTH_NEED,
                                              "All NEED" = "all children need mental health treatment",
                                              "SOME NEED" = "some but not all children", 
                                              "NONE NEED" =  "no, none of the children",
                                              NULL = "NA"
)

summary(Household_kids$MHLTH_NEED)
```

```{r}
Household_kids$MHLTH_GET <- fct_recode(Household_kids$MHLTH_GET,
                                              "All GET" = "all children get the mental health treatment they need",
                                              "SOME GET" = "some but not all children", 
                                              "NONE GET" =  "no, none of the children",
                                              NULL = "NA"
)
summary(Household_kids$MHLTH_GET)
```

```{r}
Household_kids$SO_recode <- fct_recode(Household_kids$SEXUAL_ORIENTATION, 
                                       "Gay or Lesbian" = "gay or lesbian", 
                                       "Straight" = "straight",
                                       "Bisexual" = "bisexual",
                                       "Other" = "something else",
                                        NULL = "dont know",
                                        NULL = "NA"
) 

summary(Household_kids$SO_recode)
```

```{r}
d_SO_GET <- Household_kids %>% drop_na(SO_recode, MHLTH_GET)
```

```{r}
p <- ggplot(data = d_SO_GET,
            mapping = aes(x = MHLTH_GET, fill = SO_recode)) 

p + geom_bar(position = "dodge",
             mapping = aes(y = ..prop.., group = SO_recode))

```

```{r}
d_SO_NEED <- Household_kids %>% drop_na(SO_recode, MHLTH_NEED)
```

```{r}
p2 <- ggplot(data = d_SO_NEED,
            mapping = aes(x = MHLTH_NEED, fill = SO_recode)) 

p2 + geom_bar(position = "dodge",
             mapping = aes(y = ..prop.., group = SO_recode))

```

```{r}
Household_kids$DOWN_recode <- fct_recode(Household_kids$DOWN,
                                              "NO DAYS" = "no days in past 2 wks feeling depressed",
                                              "SEVERAL" = "several days over past 2 wks", 
                                              "MORE THAN HALF" =  "more than half the days over past 2 wks",
                                              "NEARLY EVERYDAY" =  "nearly every day",
                                              NULL = "NA"
)
```

```{r}
d_SO_Down <- Household_kids %>% drop_na(SO_recode, DOWN_recode)
```

```{r}
p3 <- ggplot(data = d_SO_Down,
            mapping = aes(x = DOWN_recode, fill = SO_recode)) 

p3 + geom_bar(position = "dodge",
             mapping = aes(y = ..prop.., group = SO_recode))

```

```{r}
Household_kids$ANXIOUS_recode <- fct_recode(Household_kids$ANXIOUS,
                                              "NO DAYS" = "no anxiety over past 2 wks",
                                              "SEVERAL" = "several days anxiety over past 2 wks", 
                                              "MORE THAN HALF" =  "more than half the days anxiety over past 2 wks",
                                              "NEARLY EVERYDAY" =  "nearly every day anxiety",
                                              NULL = "NA"
)
```

```{r}
d_SO_Anxiety <- Household_kids %>% drop_na(SO_recode, ANXIOUS_recode)
```

```{r}
p4 <- ggplot(data = d_SO_Anxiety,
            mapping = aes(x = ANXIOUS_recode, fill = SO_recode)) 

p4 + geom_bar(position = "dodge",
             mapping = aes(y = ..prop.., group = SO_recode))
```

```{r}
Householdsmall$MHLTH_recode <- cut(Householdsmall$MHLTH_NEED, breaks = c(0,1,2))
summary(Householdsmall$MHLTH_recode)
```

```{r}
Householdsmall$MHLTH_recode2 <- cut(Householdsmall$MHLTH_GET, breaks = c(0,1,2))
summary(Householdsmall$MHLTH_recode2)
```

### `LINE GRAPHS`

```{r}
plineplot1 <- ggplot(data = Householdsmall,
            mapping = aes(x = DOWN,
                          y = ANXIOUS,
                          color = SEXUAL_ORIENTATION,
                          fill = SEXUAL_ORIENTATION))

plineplot1 + geom_point() + 
  geom_smooth(method = "loess") + 
  scale_x_log10()
 

```

```{r}
plineplot1a <- ggplot(data = Householdsmall,
            mapping = aes(x = ANXIOUS,
                          y = MHLTH_GET,
                          color = SEXUAL_ORIENTATION,
                          fill = SEXUAL_ORIENTATION))

plineplot1a + geom_point() + 
  geom_smooth(method = "loess") + 
  scale_x_log10()
```



```{r}
plineplot2 <- ggplot(data = Householdsmall, 
                     mapping = aes(x = ANXIOUS,
                                   y = MHLTH_NEED,
                                   color = SEXUAL_ORIENTATION,
                                   fill = SEXUAL_ORIENTATION))
plineplot2 + geom_point() + 
  geom_smooth(method = "loess") +
  scale_x_log10()
```

```{r}
plineplot3 <- ggplot(data = Householdsmall, 
                     mapping = aes(x = DOWN,
                                   y = MHLTH_NEED,
                                   color = SEXUAL_ORIENTATION,
                                   fill = SEXUAL_ORIENTATION))
plineplot3 + geom_point() + 
  geom_smooth(method = "loess") +
  scale_x_log10()
```

```{r}
plineplot4 <- ggplot(data = Householdsmall, 
                     mapping = aes(x = DOWN,
                                   y = MHLTH_GET,
                                   color = SEXUAL_ORIENTATION,
                                   fill = SEXUAL_ORIENTATION))
plineplot4 + geom_point() + 
  geom_smooth(method = "loess") +
  scale_x_log10()
```

```{r}
plineplot5 <- ggplot(data = Householdsmall, 
                     mapping = aes(x = ANXIOUS,
                                   y = MHLTH_GET,
                                   color = SEXUAL_ORIENTATION,
                                   fill = SEXUAL_ORIENTATION))
plineplot5 + geom_point() + 
  geom_smooth(method = "loess") +
  scale_x_log10()
```


### `LM/ANOVA (LOGISTIC)`



```{r}
model_1b <- lm(MHLTH_GET ~ SEXUAL_ORIENTATION, data = Householdsmall)
stargazer(model_1b, type = "text")
```


```{r}
model_2 <- lm(MHLTH_GET ~ SEXUAL_ORIENTATION*MHLTH_DIFFCLT + GENID_DESCRIBE + I(DOWN^2), data = Householdsmall)
stargazer(model_2, type = "text")
```



```{r}
model_3 <- lm(MHLTH_NEED ~ SEXUAL_ORIENTATION*MHLTH_DIFFCLT + GENID_DESCRIBE + DOWN, data = Householdsmall)
stargazer(model_3, type = "text")
```



```{r}
model_4 <- lm(MHLTH_NEED ~ SEXUAL_ORIENTATION*MHLTH_DIFFCLT + GENID_DESCRIBE + I(ANXIOUS^2), data = Householdsmall)
stargazer(model_4, type = "text")
```

```{r}
model_5 <- lm(MHLTH_GET ~ SEXUAL_ORIENTATION*MHLTH_DIFFCLT + GENID_DESCRIBE + ANXIOUS, data = Householdsmall)
stargazer(model_5, type = "text")
```


```{r}
to_be_predicted_1 <- data.frame(SEXUAL_ORIENTATION = "bisexual",  MHLTH_DIFFCLT = "unable to get treatment due to difficulty",
                        GENID_DESCRIBE = "male", DOWN = 0:3)

to_be_predicted_1$yhat1 <- predict(model_2, newdata = to_be_predicted_1)
to_be_predicted_1$yhat2 <- predict(model_3, newdata = to_be_predicted_1)

anova(model_2,model_3)
```

```{r}
to_be_predicted_2 <- data.frame(SEXUAL_ORIENTATION = "bisexual",  MHLTH_DIFFCLT = "unable to get treatment due to difficulty",
                        GENID_DESCRIBE = "male", ANXIOUS = 0:3)

to_be_predicted_2$yhat3 <- predict(model_4, newdata = to_be_predicted_2)
to_be_predicted_2$yhat4 <- predict(model_5, newdata = to_be_predicted_2)

anova(model_4,model_5)
```


```{r}
d_for_graphing <- data.frame(DOWN = 0:3, 
                             to_be_predicted_1$yhat1,
                             to_be_predicted_1$yhat2)

p_predvals <- ggplot(d_for_graphing, aes(DOWN))
p_predvals + geom_line(aes(y = to_be_predicted_1.yhat1), color = 'blue') +
  geom_line(aes(y = to_be_predicted_1.yhat2), color = 'red')
```

```{r}
d2_for_graphing <- data.frame(ANXIOUS = 0:3, 
                             to_be_predicted_2$yhat3,
                             to_be_predicted_2$yhat4)

p2_predvals <- ggplot(d2_for_graphing, aes(ANXIOUS))

p2_predvals + geom_line(aes(y = to_be_predicted_2.yhat3), color = 'orange') +
  geom_line(aes(y = to_be_predicted_2.yhat4), color = 'green')
```


### `OLS MODELS`

```{r}
select3 <- (Householdsmall$MHLTH_NEED != "NA")
d_smallneed <- subset(Householdsmall, select3)
```

```{r}
select4 <- (Householdsmall$MHLTH_GET !="NA")
d_smallget <-subset(Householdsmall, select4)
```

```{r}
d_smallneed$MentHealthKids <- as.numeric( 
  (d_smallneed$MHLTH_NEED == "1") |
  (d_smallneed$MHLTH_NEED == "2") )
```

```{r}
ols_out1 <- lm(MHLTH_NEED ~ -1 + DOWN + ANXIOUS + SEXUAL_ORIENTATION, data = d_smallneed)
stargazer(ols_out1, type = "text")
```



```{r}
ols_out1a <- lm(DOWN ~ MHLTH_NEED-1 + DOWN + ANXIOUS + SEXUAL_ORIENTATION + MHLTH_DIFFCLT + MHLTH_SATISFD, data = d_smallneed)
stargazer(ols_out1a, type = "text")
```

```{r}
ols_out1b <- lm(ANXIOUS ~ -1 + MHLTH_NEED + ANXIOUS + SEXUAL_ORIENTATION*SOCIAL1 , data = d_smallneed)
stargazer(ols_out1b, type = "text")
```

```{r}
ols_out1c <- lm(MHLTH_NEED ~ -1 + DOWN + ANXIOUS + SEXUAL_ORIENTATION* KINDWORK , data = d_smallneed)
stargazer(ols_out1c, type = "text")
```

```{r}
ols_out1d <- lm(MHLTH_NEED ~ -1 + DOWN + ANXIOUS + SEXUAL_ORIENTATION + ENROLLNONE + MHLTH_DIFFCLT , data = d_smallneed)
stargazer(ols_out1d, type = "text")
```

```{r}
ols_out2 <- lm(MHLTH_GET ~ -1 + DOWN + ANXIOUS + SEXUAL_ORIENTATION + MHLTH_DIFFCLT + MHLTH_SATISFD, data = d_smallneed)
stargazer(ols_out2, type = "text")
```

```{r}
ols_out2a <- lm(MHLTH_GET ~ -1 + DOWN + ANXIOUS + SEXUAL_ORIENTATION*SOCIAL1, data = d_smallneed)
stargazer(ols_out2a, type = "text")
```

```{r}
ols_out2b <- lm(MHLTH_GET ~ -1 + DOWN + ANXIOUS + SEXUAL_ORIENTATION + KINDWORK, data = d_smallneed)
stargazer(ols_out2b, type = "text")
```

```{r}
ols_out2c <- lm(MHLTH_GET ~ -1 + DOWN + ANXIOUS + SEXUAL_ORIENTATION + ENROLLNONE, data = d_smallneed)
stargazer(ols_out2c, type = "text")
```

```{r}
p_avg_byenrolled <- ggplot(d_SO_Anxiety, aes(x =SO_recode, fill = MHLTH_NEED))

p_avg_byenrolled + geom_bar(position = "fill", width = 0.7) + scale_fill_viridis_d(option = "mako", begin = 0.3, end = 0.85) + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + facet_grid(~ENROLLNONE)
```

```{r}
p_avg_bywork <- ggplot(d_SO_Anxiety, aes(x =SO_recode, fill = MHLTH_NEED))

p_avg_bywork + geom_bar(position = "fill", width = 0.7) + scale_fill_viridis_d(option = "mako", begin = 0.3, end = 0.85) + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + facet_grid(~KINDWORK)
```

```{r}
p_avg_bysocial <- ggplot(d_SO_Down, aes(x =SO_recode, fill = MHLTH_NEED))

p_avg_bysocial + geom_bar(position = "fill", width = 0.7) + scale_fill_viridis_d(option = "mako", begin = 0.3, end = 0.85) + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + facet_grid(~SOCIAL1)
```

```{r}
p_avg_bymhdiff <- ggplot(d_SO_Down, aes(x =SO_recode, fill = MHLTH_NEED))

p_avg_bymhdiff + geom_bar(position = "fill", width = 0.7) + scale_fill_viridis_d(option = "mako", begin = 0.3, end = 0.85) + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + facet_grid(~MHLTH_DIFFCLT)
```


```{r}
xtabs (~ d_SO_Down$MHLTH_NEED  + d_SO_Down$SEXUAL_ORIENTATION + d_SO_Down$DOWN)
``` 






### `DEPRESSION TREE MODEL`

```{r}
select <- (Household_Pulse_data$DOWN != "NA")

Household_down <- subset(Household_Pulse_data, select)
Household_down$DOWN <- fct_drop(Household_down$DOWN)
```

```{r}
Household_down$down_recode <- as.numeric( 
  (Household_down$DOWN == "several days over past 2 wks") |
    (Household_down$DOWN == "more than half the days over past 2 wks") | 
    (Household_down$DOWN == "nearly every day") )
```

```{r}
down_for_tree <- select(Household_down, -DOWN)

tree_mod1 <- rpart(down_recode ~ ., data = Household_down, method = "class", cp = 0.01)
tree_mod1
```

```{r}
rpart.plot(tree_mod1)
```

```{r}
down_for_tree2 <- select(down_for_tree, - ANXIOUS, - MHLTH_NEED, - MHLTH_GET, - SEXUAL_ORIENTATION)

tree_mod2 <- rpart(down_recode ~ ., data = down_for_tree2, method = "class", cp = 0.0021)
tree_mod2

```

```{r}
rpart.plot(tree_mod2)
```

### `ANXIETY TREE MODEL`

```{r}
select2 <- (Household_Pulse_data$ANXIOUS != "NA")

Household_anxious <- subset(Household_Pulse_data, select2)
Household_anxious$ANXIOUS <- fct_drop(Household_anxious$ANXIOUS)
```

```{r}
Household_anxious$anxious_recode <- as.numeric( 
  (Household_anxious$ANXIOUS == "several days anxiety over past 2 wks") |
    (Household_anxious$ANXIOUS == "more than half the days anxiety over past 2 wks") | 
    (Household_anxious$ANXIOUS == "nearly every day anxiety") )
```

```{r}
anxious_for_tree <- select(Household_anxious, -ANXIOUS)

tree_mod3 <- rpart(anxious_recode ~ ., data = Household_anxious, method = "class", cp = 0.001)
tree_mod3
```

```{r}
rpart.plot(tree_mod3)
```

```{r}
anxious_for_tree2 <- select(anxious_for_tree, - DOWN, - MHLTH_NEED, - MHLTH_GET, - SEXUAL_ORIENTATION)

tree_mod4 <- rpart(down_recode ~ ., data = down_for_tree2, method = "class", cp = 0.0021)
tree_mod4

```

```{r}
rpart.plot(tree_mod4)
```

### `KNN`


```{r}

NN <- length(Household_Pulse_data$SEXUAL_ORIENTATION)
set.seed(12345)
restrict_1 <- (runif(NN) < 0.3)
summary(restrict_1)
```


```{r}
Householdsmall <- subset(Household_Pulse_data, restrict_1)
```

DOWN:Level Re-code (Add this Code!)

```{r}
levels(Householdsmall$DOWN) <- c(levels(Householdsmall$DOWN), "several/more than half")
```

```{r}
Householdsmall$DOWN[Householdsmall$DOWN %in% c("several days over past 2 wks", "more than half the days over past 2 wks")] <- "several/more than half"
```

```{r}
Householdsmall$DOWN <- droplevels(Householdsmall$DOWN)
```

ANXIOUS:Level Re-code

```{r}
levels(Householdsmall$ANXIOUS) <- c(levels(Householdsmall$ANXIOUS), "several/more than half")
```

```{r}
Householdsmall$ANXIOUS[Householdsmall$ANXIOUS %in% c("several days anxiety over past 2 wks", "more than half the days anxiety over past 2 wks")] <- "several/more than half"
```

```{r}
Householdsmall$ANXIOUS <- droplevels(Householdsmall$ANXIOUS)
```

Sexual Orientation: Level Re-code

```{r}
levels(Householdsmall$SEXUAL_ORIENTATION) <- c(levels(Householdsmall$SEXUAL_ORIENTATION), "LGBTQ")
```

```{r}
Householdsmall$SEXUAL_ORIENTATION[Householdsmall$SEXUAL_ORIENTATION %in% c("gay or lesbian", "bisexual")] <- "LGBTQ"
```

```{r}
Householdsmall$SEXUAL_ORIENTATION <- droplevels(Householdsmall$SEXUAL_ORIENTATION)
```


### Actual KNN:

Factor Re-codes:

DOWN-

```{r}
Householdsmall$DOWN_recode <- fct_recode(Householdsmall$DOWN, 
                                        "0" = "no days in past 2 wks feeling depressed",
                                "0.5" = "several/more than half", 
                                "1" = "nearly every day",
                                NULL = "NA"
)

Householdsmall$DOWN_recode <- as.numeric(as.character(Householdsmall$DOWN_recode))[Householdsmall$DOWN_recode]
```

ANXIOUS
```{r}
Householdsmall$ANXIOUS_recode <- fct_recode(Householdsmall$ANXIOUS, 
                                        "0" = "no anxiety over past 2 wks",
                                "0.5" = "several/more than half", 
                                "1" = "nearly every day anxiety",
                                NULL = "NA"
)

Householdsmall$ANXIOUS_recode <- as.numeric(as.character(Householdsmall$ANXIOUS_recode))[Householdsmall$ANXIOUS_recode]
```

SEXUAL_ORIENTATION

```{r}
Householdsmall$SEXUAL_ORIENTATION_recode <- fct_recode(Householdsmall$SEXUAL_ORIENTATION, 
                                        "0" = "straight",
                                "0.5" = "something else", 
                                "1" = "LGBTQ",
                                NULL = "NA"
)

Householdsmall$SEXUAL_ORIENTATION_recode <- as.numeric(as.character(Householdsmall$SEXUAL_ORIENTATION_recode))[Householdsmall$SEXUAL_ORIENTATION_recode]
```

MHLTH_GET

```{r}
Householdsmall$MHLTH_GET_recode <- fct_recode(Householdsmall$MHLTH_GET, 
                                        "0" = "no, none of the children",
                                "0.5" = "some but not all children", 
                                "1" = "all children get the mental health treatment they need",
                                NULL = "NA"
)

Householdsmall$MHLTH_GET_recode <- as.numeric(as.character(Householdsmall$MHLTH_GET_recode))[Householdsmall$MHLTH_GET_recode]
```

Fingers Crossed:

```{r}
Householdsmall$MHLTH_NEED <- recode(Householdsmall$MHLTH_NEED, "NA" = NULL, "all children need mental health treatment" = 0, "some but not all children" = 1, "no, none of the children" = 2)
```

```{r}
standardize_varb_to01 <- function(X_in) {
  (X_in - min(X_in, na.rm = TRUE))/( max(X_in, na.rm = TRUE) - min(X_in, na.rm = TRUE)  )
}
```

```{r}
X1 <- Householdsmall$DOWN_recode
X2 <- Householdsmall$ANXIOUS_recode
X3 <- Householdsmall$SEXUAL_ORIENTATION_recode
X4 <- Householdsmall$MHLTH_GET_recode

Y <- Householdsmall$MHLTH_NEED

nonmissingobs <- complete.cases(Y,X1,X2,X3,X4)

X1 <- subset(X1, nonmissingobs)
X2 <- subset(X2, nonmissingobs)
X3 <- subset(X3, nonmissingobs)
X4 <- subset(X4, nonmissingobs)
dat_use <- data.frame(X1,X2,X3,X4)
Y <- subset(Y, nonmissingobs)
```

```{r}
set.seed(1234)
NN_obs <- length(Y)
select1 <- (runif(NN_obs) < 0.6)
train_data <- subset(dat_use,select1)
test_data <- subset(dat_use,(!select1))
cl_data <- Y[select1]
true_data <- Y[!select1]
```

```{r}
library(caret)
library(dplyr)

require(caret)
require(dplyr)


for (indx in seq(1, 9, by= 2)) {
pred_y <- knn3Train(train_data, test_data, cl_data, k = indx, l = 0, prob = FALSE, use.all = TRUE)
num_correct_labels <- sum(pred_y == true_data)
correct_rate <- num_correct_labels/length(true_data)
 print(c(indx, correct_rate))
}
```

## `CORRELATION GRAPHS`

```{r}
p_avg_byGET <- ggplot(d_SO_GET, aes(x = MHLTH_GET, fill = MHLTH_NEED))

p_avg_byGET + geom_bar(position = "fill", width = 0.7) + scale_fill_viridis_d(option = "mako", begin = 0.3, end = 0.85) + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + facet_grid(~SO_recode)
```

```{r}
p_avg_byDown <- ggplot(d_SO_Down, aes(x = DOWN_recode, fill = MHLTH_NEED))

p_avg_byDown + geom_bar(position = "fill", width = 0.7) + scale_fill_viridis_d(option = "mako", begin = 0.3, end = 0.85) + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + facet_grid(~SO_recode)
```

```{r}
p_avg_byAnxiety <- ggplot(d_SO_Anxiety, aes(x = ANXIOUS_recode, fill = MHLTH_NEED))

p_avg_byAnxiety + geom_bar(position = "fill", width = 0.7) + scale_fill_viridis_d(option = "mako", begin = 0.3, end = 0.85) + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + facet_grid(~SO_recode)
```

```{r}
g_SO_Down <- Household_kids %>% drop_na(SO_recode, DOWN_recode, MHLTH_GET)
```

```{r}
g_avg_byDown <- ggplot(g_SO_Down, aes(x = DOWN_recode, fill = MHLTH_GET))

g_avg_byDown + geom_bar(position = "fill", width = 0.7) + scale_fill_viridis_d(option = "mako", begin = 0.3, end = 0.85) + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + facet_grid(~SO_recode)
```
```{r}
g_SO_Anxiety <- Household_kids %>% drop_na(SO_recode, ANXIOUS_recode, MHLTH_GET)
```

```{r}
g_SO_Anxiety <- ggplot(g_SO_Down, aes(x = DOWN_recode, fill = MHLTH_GET))

g_SO_Anxiety + geom_bar(position = "fill", width = 0.7) + scale_fill_viridis_d(option = "mako", begin = 0.3, end = 0.85) + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + facet_grid(~SO_recode)
```













